Make any stupid plot you want

### 2021-02-15 draft/sections/next.tex
trying to compile next + fixed some errors
half of limitations para

The toy prototype built using this model validates that is usable for a general purpose visualization tool since it can be iteratively integrated into the existing architecture rather than starting from scratch/ Factoring out glyph formation into assembly functions allows for much more clarity in how the glyphs differ. This prototype demonstrates that this framework can generate the fundemental marks, point (scatter plot), line (line chart), and area (bar chart). Furthermore, the grouped and stacked bar examples demonstrate that this model supports composition of glyphs into more complex graphics. These composite examples also rely on the fiber bundles section base book keeping to keep track of which components contribute to the attributes of the glyph. Implementing this example using a Pandas dataframe demonstrates the ease of incorporating existing widely used data containers rather than requiring users to conform to one stands.  
\subsection{What are the limitations?}
%%%An interesting control problem will be how to keep the text and graphics consistent. If the rendering exchanges the horizontal and vertical axes of a bar chart, the text must also exchange its references to the axes.
\begin{itemize}
\item is at arc level
\item is at one dataset level - needs invariants/composites
\item static (what happens with interactive - but this is just update )
\item is compose(encodes) and ggplot is plot(encodes, glyph)
\item can't handle figerative/semantic equivariance (this actually could maybe be done as extension of fber)
\item explicitely does not care about effectiveness - is domain specific 
\item is only developed against Matplotlib
\item is written against AGG/SVG
\item layout
\item text
\item same as APT, is at gd level so cannot control render 
\item keeping all data in sync if transform is changed in one place (so on multi composed graphs, changing x on does it propopgate - part of Bertin invariance)
\end{itemize}
\subsection{What else needs to be implemented?}
\begin{itemize}
    \item heatmaps/ proof of concept of face simplex
    \item composition algebra
    \item boxplot - multiglyph composition
    \item debatable: non-trivial bundle like data on mobius backend
    \item interactivity 
    \item concurrent artist
    \item numpy wrapper
\end{itemize}
\begin{itemize}
    \item provisional implementation using new architecture in Matplotlib
    \item developer-aimed documentation (API + narrative)
    \item proof of concept 3rd party user-facing library with a biology partner
    \item academic paper about building visualization tools on top of the core architecture
\end{itemize}
Other things that may or may not play a big role would be working out the details of the S->K interaction for dashboards. By this I particularly mean when S is a composite object spanning all the figures shown in the dashboard and a component of K may have different compoents of S mapping into it slicing it in different ways.
\subsection{What are the lessons learned?}

>>>>

The toy prototype built using this model validates that is usable for a general purpose visualization tool since it can be iteratively integrated into the existing architecture rather than starting from scratch/ Factoring out glyph formation into assembly functions allows for much more clarity in how the glyphs differ. This prototype demonstrates that this framework can generate the fundemental marks, point (scatter plot), line (line chart), and area (bar chart). Furthermore, the grouped and stacked bar examples demonstrate that this model supports composition of glyphs into more complex graphics. These composite examples also rely on the fiber bundles section base book keeping to keep track of which components contribute to the attributes of the glyph. Implementing this example using a Pandas dataframe demonstrates the ease of incorporating existing widely used data containers rather than requiring users to conform to one stands.

\subsection{What are the limitations?}
%%%An interesting control problem will be how to keep the text and graphics consistent. If the rendering exchanges the horizontal and vertical axes of a bar chart, the text must also exchange its references to the axes.
So far this model has only been worked out for a single data set tied to a primitive mark, but it should be extensible to compositing datasets and complex glyphs. The examples and prototype have so far only been implemented for the static 2D case, but nothing in the math limits to 2D and expansion to the animated case should be possible because the model is formalized in terms of the sheaf. Since it is a purely mathematical framework, this model does not have a way to model or check for semantic equivariance of figurative representations, but this could be an avenue of research for machine learning researchers.

\begin{itemize}

\item can't handle figerative/semantic equivariance (this actually could maybe be done as extension of fber)
\item explicitely does not care about effectiveness - is domain specific 
\item is only developed against Matplotlib
\item is written against AGG/SVG
\item layout
\item text
\item same as APT, is at gd level so cannot control render 
\item keeping all data in sync if transform is changed in one place (so on multi composed graphs, changing x on does it propopgate - part of Bertin invariance)
\end{itemize}

\subsection{What else needs to be implemented?}
\begin{itemize}
    \item is compose(encodes) and ggplot is plot(encodes, glyph)
    \item heatmaps/ proof of concept of face simplex
    \item composition algebra
    \item boxplot - multiglyph composition
    \item debatable: non-trivial bundle like data on mobius backend
    \item interactivity 
    \item concurrent artist
    \item numpy wrapper
\end{itemize}
\begin{itemize}
    \item provisional implementation using new architecture in Matplotlib
    \item developer-aimed documentation (API + narrative)
    \item proof of concept 3rd party user-facing library with a biology partner
    \item academic paper about building visualization tools on top of the core architecture
\end{itemize}

Other things that may or may not play a big role would be working out the details of the S->K interaction for dashboards. By this I particularly mean when S is a composite object spanning all the figures shown in the dashboard and a component of K may have different compoents of S mapping into it slicing it in different ways.
\subsection{What are the lessons learned?}
